Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
typo

A discrete-time linear system is said to be Bounded-Input and Bounded-Output
(BIBO) stable if and only if every pole of its transfer function lies inside
the unit circle.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
lemma states necessary conditions for BIBO stability of the closed-loop system
in Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
$\nu_{1}$, and $\nu_{2}$ are bounded.

>>>>

A discrete-time linear system is said to be Bounded-Input and Bounded-Output
(BIBO) stable if and only if every pole of its transfer function lies inside
the unit circle.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
lemma states necessary conditions for BIBO stability of the closed-loop system
in Figure~\ref{fig:sampledsystem}, since the exogenous signals $R(z)$,
$\nu_{1}$, and $\nu_{2}$ are bounded.
